\begin{thebibliography}{9}

\bibitem{LHCDesign}
O. S. Bruning et al. 
\textit{LHC design report, Volume 1}
CERN, Geneva. (2004)

\bibitem{ATLASExperiment}
The ATLAS Collaboration.
\textit{The ATLAS experiment at the CERN Large Hadron Collider.}
J. Instrum. 3, S08003 (2008).

\bibitem{ATLASDetector}
The ATLAS Collaboration.
\textit{The ATLAS detector and physics performance: Technical design report.}
CERN, Geneva. (1999).

\bibitem{ATLASMagnets}
The ATLAS Collaboration.
\textit{ATLAS magnet system: Technical Design Report, 1.}
CERN, Geneva. (1997).

\bibitem{ATLASInnerDet}
The ATLAS Collaboration
\textit{ATLAS Inner Detector: Technical Design Report, Vol. 1.}
CERN, Geneva. (1997).

\bibitem{ATLASCal}
H. Wilkens, (The ATLAS LArg Collaboration)
\textit{The ATLAS Liquid Argon Calorimeter: an overview.}
IOP Publishing. Journal of Physics: Conference Series 160, 012043 (2009).

\bibitem{ATLASMuon}
The ATLAS Collaboration
\textit{ATLAS muon spectrometer: Technical Design Report}
CERN, Geneva. (1997).

\bibitem{JER2010}
The ATLAS Collaboration
\textit{Jet energy resolution in proton-proton collisions at COM = 7 TeV recorded in 2010 with the ATLAS detector}
CERN, Geneva. (2012).

\bibitem{JER2012}
The ATLAS Collaboration
\textit{Data-driven determination of the energy scale and resolution of jets reconstructed in the ATLAS calorimeters using dijet and multijet events at COM = 8 TeV.}
CERN, Geneva. (2015).

\bibitem{DMIntrobook}
D. Majumdar. (Saha Institute of Nuclear Physics, Calcutta, India.)
\textit{Dark Matter: An Introduction}
CRC Press, Taylor and Francis Group, NY. (2014).

\bibitem{VeraRubin}
V. Rubin and Y. Sofue.
\textit{Rotation Curves of Spiral Galaxies}
Annual Review of Astronomy and Astrophysics, Vol. 39. (2001).

\bibitem{rotationcurveplot}
A. G. Doroshkevich et al. 
\textit{A solution to the problems of cusps and rotation curves in dark matter halos in the cosmological standard model.}
Phys. Usp. Vol. 55. (2012).

\bibitem{DMDepthbook}
G. Bertone. (Paris Institute of Astrophysics)
\textit{Particle Dark Matter: Observations, Models and Searches.}
 Cambridge University Press, NY. (2010).

\bibitem{bulletcluster}
D. Clowe et al.
\textit{A Direct Empirical Proof of the Existence of Dark Matter.}
ApJ Letters in Press. (2004).

\bibitem{DarkMatterSearches}
L. Baudis.
\textit{Dark Matter Searches}
Annual Physics. Berlin, 1-10. (2015).

\bibitem{MG}
J. Alwall et al.
\textit{The automated computation of tree-level and next-to-leading order differential cross sections, and their matching to parton shower simulations}
hep-ph 07 079. (2014).

\bibitem{Lagrangian}
R. C. Cotta et al.
\textit{Bounds on Dark Matter Interactions with Electroweak Gauge Bosons.}
SLAC National Accelerator Laboratory, USA. (2012).

\bibitem{Rivet}
A. buckley et al. 
\textit{Rivet user manual.}
hep-ph. (2013).

\end{thebibliography}
